%Rozdział 2.
\bibitem{Macal2010} Macal, C. M., \& North, M. J. (2010). Tutorial on agent-based modelling and simulation. \textit{Journal of Simulation}, 4(3), 151-162.
\bibitem{Tesfatsion2006} Tesfatsion, L., \& Judd, K. L. (Eds.). (2006). \textit{Handbook of Computational Economics: Agent-Based Computational Economics} (Vol. 2). Elsevier.
\bibitem{Epstein2007} Epstein, J. M. (2007). \textit{Generative Social Science: Studies in Agent-Based Computational Modeling}. Princeton University Press.
\bibitem{Grimm2005} Grimm, V., \& Railsback, S. F. (2005). \textit{Individual-based Modeling and Ecology}. Princeton University Press.
\bibitem{Bonabeau2002} Bonabeau, E. (2002). Agent-based modeling: Methods and techniques for simulating human systems. \textit{Proceedings of the National Academy of Sciences}, 99 (Suppl 3), 7280-7287.
\bibitem{Eubank2004} Eubank, S., Guclu, H., Kumar, V. S. A., Marathe, M. V., Srinivasan, A., Toroczkai, Z., \& Wang, N. (2004). Modelling disease outbreaks in realistic urban social networks. \textit{Nature}, 429 (6988), 180-184.

\bibitem{Wasserman1994} Wasserman, S., \& Faust, K. (1994). \textit{Social Network Analysis: Methods and Applications}. Cambridge University Press.
\bibitem{Newman2010} Newman, M. E. J. (2010). \textit{Networks: An Introduction}. Oxford University Press.
\bibitem{Girvan2002} Girvan, M., \& Newman, M. E. J. (2002). Community structure in social and biological networks. \textit{Proceedings of the National Academy of Sciences}, 99 (12), 7821-7826.
\bibitem{Freeman1979} Freeman, L. C. (1979). Centrality in social networks: Conceptual clarification. \textit{Social Networks}, 1(3), 215-239.
\bibitem{Hanneman2005} Hanneman, R. A., \& Riddle, M. (2005). \textit{Introduction to Social Network Methods}. University of California.
\bibitem{Scott2000} Scott, J. (2000). \textit{Social Network Analysis: A Handbook} (2nd ed.). SAGE Publications.
\bibitem{Borgatti1997} Borgatti, S. P., \& Everett, M. G. (1997). Network analysis of two-mode data. \textit{Social Networks}, 19(3), 243-269.
\bibitem{Holme2012} Holme, P., \& Saramäki, J. (2012). Temporal networks. \textit{Physics Reports}, 519(3), 97-125.

\bibitem{Erdos1959} Erdős, P., \& Rényi, A. (1959). On Random Graphs I. \textit{Publicationes Mathematicae}, 6, 290-297.
\bibitem{Erdos1960} Erdős, P., \& Rényi, A. (1960). On the evolution of random graphs. \textit{Publ. Math. Inst. Hung. Acad. Sci}, 5, 17-60.
\bibitem{Newman2003} Newman, M. E. J. (2003). The structure and function of complex networks. \textit{SIAM Review}, 45(2), 167-256.
\bibitem{Watts1998} Watts, D. J., \& Strogatz, S. H. (1998). Collective dynamics of 'small-world' networks. \textit{Nature}, 393(6684), 440-442.
\bibitem{Bollobas2001} Bollobás, B. (2001). \textit{Random Graphs}. Cambridge University Press.
\bibitem{Barabasi1999} Barabási, A.-L., \& Albert, R. (1999). Emergence of scaling in random networks. \textit{Science}, 286(5439), 509-512.

\bibitem{Albert2002} Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex networks. \textit{Reviews of Modern Physics}, 74(1), 47-97.
\bibitem{Albert2000} Albert, R., Jeong, H., \& Barabási, A.-L. (2000). Error and attack tolerance of complex networks. \textit{Nature}, 406(6794), 378-382.
\bibitem{Barabasi2003} Barabási, A.-L., \& Bonabeau, E. (2003). Scale-free networks. \textit{Scientific American}, 288(5), 60-69.
\bibitem{Jeong2000} Jeong, H., Tombor, B., Albert, R., Oltvai, Z. N., \& Barabási, A.-L. (2000). The large-scale organization of metabolic networks. \textit{Nature}, 407(6804), 651-654.
\bibitem{Battiston2007} Battiston, S., Delli Gatti, D., Gallegati, M., Greenwald, B., \& Stiglitz, J. E. (2007). Credit chains and bankruptcy propagation in production networks. \textit{Journal of Economic Dynamics and Control}, 31(6), 2061-2084.
\bibitem{Price1976} Price, D. J. de S. (1976). A general theory of bibliometric and other cumulative advantage processes. \textit{Journal of the American Society for Information Science}, 27(5), 292-306.
\bibitem{Leskovec2008} Leskovec, J., Lang, K. J., Dasgupta, A., \& Mahoney, M. (2008). Statistical properties of community structure in large social and information networks. \textit{Proceedings of the 17th International Conference on World Wide Web}, 695-704.
\bibitem{Pastor2001} Pastor-Satorras, R., \& Vespignani, A. (2001). Epidemic spreading in scale-free networks. \textit{Physical Review Letters}, 86(14), 3200-3203.
\bibitem{Klemm2002} Klemm, K., \& Eguiluz, V. M. (2002). Highly clustered scale-free networks. \textit{Physical Review E}, 65(3), 036123.
\bibitem{Amaral2000} Amaral, L. A. N., Scala, A., Barthelemy, M., \& Stanley, H. E. (2000). Classes of small-world networks. \textit{Proceedings of the National Academy of Sciences}, 97(21), 11149-11152.
\bibitem{Dorogovtsev2002} Dorogovtsev, S. N., \& Mendes, J. F. F. (2002). Evolution of networks. \textit{Advances in Physics}, 51(4), 1079-1187.
\bibitem{Boccaletti2006} Boccaletti, S., Latora, V., Moreno, Y., Chavez, M., \& Hwang, D.-U. (2006). Complex networks: Structure and dynamics. \textit{Physics Reports}, 424(4-5), 175-308.
\bibitem{Holme2002} Holme, P., Kim, B. J., Yoon, C. N., \& Han, S. K. (2002). Attack vulnerability of complex networks. \textit{Physical Review E}, 65(5), 056109.

\bibitem{Sporns2004} Sporns, O., \& Zwi, J. D. (2004). The small world of the cerebral cortex. \textit{Neuroinformatics}, 2(2), 145-162.
\bibitem{Barrat2004} Barrat, A., Barthelemy, M., Pastor-Satorras, R., \& Vespignani, A. (2004). The architecture of complex weighted networks. \textit{Proceedings of the National Academy of Sciences}, 101(11), 3747-3752.

\bibitem{Nolan1971} Nolan, D. (1971). The Case for a Libertarian Political Party. \textit{The Individualist}, 1(4), 3-6.
\bibitem{Rothbard1978} Rothbard, M. N. (1978). Libertarianism vs. the Nolan chart. \textit{Libertarian Review}, 7(1), 15-16.
\bibitem{Kirsch2020} Kirsch, A. (2020). The Nolan chart: a reconsideration of its validity and use in modern political analysis. \textit{Journal of Political Ideologies}, 25(3), 345-364.

% Rozdział 4.
\bibitem{NetworkX} Hagberg, A. A., Schult, D. A., \& Swart, P. J. (2008). Exploring network structure, dynamics, and function using NetworkX. In \textit{Proceedings of the 7th Python in Science Conference (SciPy2008)} (pp. 11-15). \url{https://networkx.org/}
\bibitem{Matplotlib} Hunter, J. D. (2007). Matplotlib: A 2D graphics environment. \textit{Computing in Science \& Engineering}, 9(3), 90-95. \url{https://matplotlib.org/}
\bibitem{CSV} Python Software Foundation. (n.d.). \textit{csv – CSV File Reading and Writing}. Python Documentation. \url{https://docs.python.org/3/library/csv.html}

% Rozdział 6.
\bibitem{rozklad_trojkatny_wykres} CC BY-SA 3.0, https://commons.wikimedia.org/w/index.php?curid=182090
\bibitem{rozklad_wykladniczy_wykres} Autorstwa Cburnett - Praca własna, CC BY-SA 3.0, \\https://commons.wikimedia.org/w/index.php?curid=73793
\bibitem{research_results} Opracowanie własne, \url{https://uniwersytetlodzki-my.sharepoint.com/personal/ul0237204_edu_uni_lodz_pl/_layouts/15/onedrive.aspx?id=%2Fpersonal%2Ful0237204%5Fedu%5Funi%5Flodz%5Fpl%2FDocuments%2Fmaster%5Fdegree%5F%2D%5Fsocial%5Fnetworking&ga=1}